---
title: "HW 1"
output: github_document
---

PROBLEM 1

Load libraries
```{r}
library(moderndive)

library(tidyverse)
```

Load dataset
```{r}
data("early_january_weather")
```

Find mean temperature
```{r}
df=early_january_weather 
mean(df$temp)

summary(early_january_weather)
```

There are 15 variables in this dataset, which include origin, year, month, day, hour, and temperature. 
The number of rows in the dataset is `r nrow(early_january_weather)`.
The number of columns in the dataset is `r ncol(early_january_weather)`.
The mean temperature is `r mean(df$temp)`.


Make scatterplot
```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color=humid)) + geom_point()

```
The scatterplot shows that temperature increases as POSIXct data increases. In addition, humidity generally increases as both temperature and POSIXct data increases. 

Save scatterplot to project directory
```{r}
ggsave("scatterplot.pdf")
```

PROBLEM 2

Create dataframe

```{r}
p2_df = tibble(
  norm_samp = rnorm(10, sd=1),
  vec_logical = norm_samp > 0,
  vec_char <- c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_factor <- factor(rep(c("Level1", "Level2", "Level3"), length.out = 10))
  )
```

Find means of each variable in p2_df

```{r}
mean(pull(p2_df, norm_samp))
mean(pull(p2_df, vec_logical))
```

```{r, eval=FALSE}
mean(pull(p2_df, vec_char))
mean(pull(p2_df, vec_factor))
```

The code does not work when trying to determine the means of the character vector and factor vector. 

```{r, eval=FALSE}
as.numeric(pull(p2_df, vec_logical))
as.numeric(pull(p2_df, vec_char))
as.numeric(pull(p2_df, vec_factor))
```

The code does not work when trying to convert the character vector and factor vector. This is because these vectors do not have column names. 


